---
title: "615 Final EDA"
author: "Ruiyi Feng"
date: "2022-12-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
```

## EDA

### Data Processing 

```{r}
setwd("~/Downloads")
dataq4 <- read.csv("HRTravelTimesQ4_21.csv") 
# Data for orange line in the fourth quarter of 2021
dataq4_orange <- filter(dataq4,route_id == "Orange") 
```

```{r}
setwd("~/Downloads/TravelTimes_2022")
dataq1 <- read.csv("2022-Q1_HRTravelTimes.csv")
# Data for orange line in the first quarter of 2022
dataq1_orange <- filter(dataq1,route_id == "Orange")

dataq2 <- read.csv("2022-Q2_HRTravelTimes.csv")
# Data for orange line in the second quarter of 2022
dataq2_orange <- filter(dataq2,route_id == "Orange")

dataq3 <- read.csv("2022-Q3_HRTravelTimes.csv")
# Data for orange line in the third quarter of 2022
dataq3_orange <- filter(dataq3,route_id == "Orange")
```

In order to make sense for the analysis,  I chose direction_id to be 0 and to_stop_id to be 70001. Then I selected the lines which had the daily latest arrival time. Dates are randomly selected. For the three months in 2021, I used the first seven days in each month. I filtered the data using same criteria for the data in 2022. I tried selecting the first seven days in each month but the first seven days does not work for data in September. Then I looked through the data for September and found seven days which could be used in the analysis. 

```{r}
# Data for October 2021
data1001 <- filter(dataq4_orange, service_date == "2021-10-01")
data1001_1 <- filter(data1001,direction_id == 0 & to_stop_id == 70001)
data1001_2 <- filter(data1001_1,end_time_sec == max(end_time_sec))

data1002 <- filter(dataq4_orange, service_date == "2021-10-02")
data1002_1 <- filter(data1002,direction_id == 0 & to_stop_id == 70001)
data1002_2 <- filter(data1002_1,end_time_sec == max(end_time_sec))

data1003 <- filter(dataq4_orange, service_date == "2021-10-03")
data1003_1 <- filter(data1003,direction_id == 0 & to_stop_id == 70001)
data1003_2 <- filter(data1003_1,end_time_sec == max(end_time_sec))

data1004 <- filter(dataq4_orange, service_date == "2021-10-04")
data1004_1 <- filter(data1004,direction_id == 0 & to_stop_id == 70001)
data1004_2 <- filter(data1004_1,end_time_sec == max(end_time_sec))

data1005 <- filter(dataq4_orange, service_date == "2021-10-05")
data1005_1 <- filter(data1005,direction_id == 0 & to_stop_id == 70001)
data1005_2 <- filter(data1005_1,end_time_sec == max(end_time_sec))

data1006 <- filter(dataq4_orange, service_date == "2021-10-06")
data1006_1 <- filter(data1006,direction_id == 0 & to_stop_id == 70001)
data1006_2 <- filter(data1006_1,end_time_sec == max(end_time_sec))

data1007 <- filter(dataq4_orange, service_date == "2021-10-07")
data1007_1 <- filter(data1007,direction_id == 0 & to_stop_id == 70001)
data1007_2 <- filter(data1007_1,end_time_sec == max(end_time_sec))

dataoct <- rbind(data1001_2,data1002_2,data1003_2,data1004_2,data1005_2,data1006_2,data1007_2)
```

```{r}
# Data for November 2021
data1101 <- filter(dataq4_orange, service_date == "2021-11-01")
data1101_1 <- filter(data1101,direction_id == 0 & to_stop_id == 70001)
data1101_2 <- filter(data1101_1,end_time_sec == max(end_time_sec))

data1102 <- filter(dataq4_orange, service_date == "2021-11-02")
data1102_1 <- filter(data1102,direction_id == 0 & to_stop_id == 70001)
data1102_2 <- filter(data1102_1,end_time_sec == max(end_time_sec))

data1103 <- filter(dataq4_orange, service_date == "2021-11-03")
data1103_1 <- filter(data1103,direction_id == 0 & to_stop_id == 70001)
data1103_2 <- filter(data1103_1,end_time_sec == max(end_time_sec))

data1104 <- filter(dataq4_orange, service_date == "2021-11-04")
data1104_1 <- filter(data1104,direction_id == 0 & to_stop_id == 70001)
data1104_2 <- filter(data1104_1,end_time_sec == max(end_time_sec))

data1105 <- filter(dataq4_orange, service_date == "2021-11-05")
data1105_1 <- filter(data1105,direction_id == 0 & to_stop_id == 70001)
data1105_2 <- filter(data1105_1,end_time_sec == max(end_time_sec))

data1106 <- filter(dataq4_orange, service_date == "2021-11-06")
data1106_1 <- filter(data1106,direction_id == 0 & to_stop_id == 70001)
data1106_2 <- filter(data1106_1,end_time_sec == max(end_time_sec))

data1107 <- filter(dataq4_orange, service_date == "2021-11-07")
data1107_1 <- filter(data1107,direction_id == 0 & to_stop_id == 70001)
data1107_2 <- filter(data1107_1,end_time_sec == max(end_time_sec))

datanov <- rbind(data1101_2,data1102_2,data1103_2,data1104_2,data1105_2,data1106_2,data1107_2)
```

```{r}
# Data for December 2021
data1201 <- filter(dataq4_orange, service_date == "2021-12-01")
data1201_1 <- filter(data1201,direction_id == 0 & to_stop_id == 70001)
data1201_2 <- filter(data1201_1,end_time_sec == max(end_time_sec))

data1202 <- filter(dataq4_orange, service_date == "2021-12-02")
data1202_1 <- filter(data1202,direction_id == 0 & to_stop_id == 70001)
data1202_2 <- filter(data1202_1,end_time_sec == max(end_time_sec))

data1203 <- filter(dataq4_orange, service_date == "2021-12-03")
data1203_1 <- filter(data1203,direction_id == 0 & to_stop_id == 70001)
data1203_2 <- filter(data1203_1,end_time_sec == max(end_time_sec))

data1204 <- filter(dataq4_orange, service_date == "2021-12-04")
data1204_1 <- filter(data1204,direction_id == 0 & to_stop_id == 70001)
data1204_2 <- filter(data1204_1,end_time_sec == max(end_time_sec))

data1205 <- filter(dataq4_orange, service_date == "2021-12-05")
data1205_1 <- filter(data1205,direction_id == 0 & to_stop_id == 70001)
data1205_2 <- filter(data1205_1,end_time_sec == max(end_time_sec))

data1206 <- filter(dataq4_orange, service_date == "2021-12-06")
data1206_1 <- filter(data1206,direction_id == 0 & to_stop_id == 70001)
data1206_2 <- filter(data1206_1,end_time_sec == max(end_time_sec))

data1207 <- filter(dataq4_orange, service_date == "2021-12-07")
data1207_1 <- filter(data1207,direction_id == 0 & to_stop_id == 70001)
data1207_2 <- filter(data1207_1,end_time_sec == max(end_time_sec))

datadec <- rbind(data1201_2,data1202_2,data1203_2,data1204_2,data1205_2,data1206_2,data1207_2)
```


```{r}
# Data for January 2022
data0101 <- filter(dataq1_orange, service_date == "2022-01-01")
data0101_1 <- filter(data0101,direction_id == 0 & to_stop_id == 70001)
data0101_2 <- filter(data0101_1,end_time_sec == max(end_time_sec))

data0102 <- filter(dataq1_orange, service_date == "2022-01-02")
data0102_1 <- filter(data0102,direction_id == 0 & to_stop_id == 70001)
data0102_2 <- filter(data0102_1,end_time_sec == max(end_time_sec))

data0103 <- filter(dataq1_orange, service_date == "2022-01-03")
data0103_1 <- filter(data0103,direction_id == 0 & to_stop_id == 70001)
data0103_2 <- filter(data0103_1,end_time_sec == max(end_time_sec))

data0104 <- filter(dataq1_orange, service_date == "2022-01-04")
data0104_1 <- filter(data0104,direction_id == 0 & to_stop_id == 70001)
data0104_2 <- filter(data0104_1,end_time_sec == max(end_time_sec))

data0105 <- filter(dataq1_orange, service_date == "2022-01-05")
data0105_1 <- filter(data0105,direction_id == 0 & to_stop_id == 70001)
data0105_2 <- filter(data0105_1,end_time_sec == max(end_time_sec))

data0106 <- filter(dataq1_orange, service_date == "2022-01-06")
data0106_1 <- filter(data0106,direction_id == 0 & to_stop_id == 70001)
data0106_2 <- filter(data0106_1,end_time_sec == max(end_time_sec))

data0107 <- filter(dataq1_orange, service_date == "2022-01-07")
data0107_1 <- filter(data0107,direction_id == 0 & to_stop_id == 70001)
data0107_2 <- filter(data0107_1,end_time_sec == max(end_time_sec))

datajan <- rbind(data0101_2,data0102_2,data0103_2,data0104_2,data0105_2,data0106_2,data0107_2)
```

```{r}
# Data for February 2022
data0201 <- filter(dataq1_orange, service_date == "2022-02-01")
data0201_1 <- filter(data0201,direction_id == 0 & to_stop_id == 70001)
data0201_2 <- filter(data0201_1,end_time_sec == max(end_time_sec))

data0202 <- filter(dataq1_orange, service_date == "2022-02-02")
data0202_1 <- filter(data0202,direction_id == 0 & to_stop_id == 70001)
data0202_2 <- filter(data0202_1,end_time_sec == max(end_time_sec))

data0203 <- filter(dataq1_orange, service_date == "2022-02-03")
data0203_1 <- filter(data0203,direction_id == 0 & to_stop_id == 70001)
data0203_2 <- filter(data0203_1,end_time_sec == max(end_time_sec))

data0204 <- filter(dataq1_orange, service_date == "2022-02-04")
data0204_1 <- filter(data0204,direction_id == 0 & to_stop_id == 70001)
data0204_2 <- filter(data0204_1,end_time_sec == max(end_time_sec))

data0205 <- filter(dataq1_orange, service_date == "2022-02-05")
data0205_1 <- filter(data0205,direction_id == 0 & to_stop_id == 70001)
data0205_2 <- filter(data0205_1,end_time_sec == max(end_time_sec))

data0206 <- filter(dataq1_orange, service_date == "2022-02-06")
data0206_1 <- filter(data0206,direction_id == 0 & to_stop_id == 70001)
data0206_2 <- filter(data0206_1,end_time_sec == max(end_time_sec))

data0207 <- filter(dataq1_orange, service_date == "2022-02-07")
data0207_1 <- filter(data0207,direction_id == 0 & to_stop_id == 70001)
data0207_2 <- filter(data0207_1,end_time_sec == max(end_time_sec))

datafeb <- rbind(data0201_2,data0202_2,data0203_2,data0204_2,data0205_2,data0206_2,data0207_2)
```

```{r}
# Data for March 2022
data0301 <- filter(dataq1_orange, service_date == "2022-03-01")
data0301_1 <- filter(data0301,direction_id == 0 & to_stop_id == 70001)
data0301_2 <- filter(data0301_1,end_time_sec == max(end_time_sec))

data0302 <- filter(dataq1_orange, service_date == "2022-03-02")
data0302_1 <- filter(data0302,direction_id == 0 & to_stop_id == 70001)
data0302_2 <- filter(data0302_1,end_time_sec == max(end_time_sec))

data0303 <- filter(dataq1_orange, service_date == "2022-03-03")
data0303_1 <- filter(data0303,direction_id == 0 & to_stop_id == 70001)
data0303_2 <- filter(data0303_1,end_time_sec == max(end_time_sec))

data0304 <- filter(dataq1_orange, service_date == "2022-03-04")
data0304_1 <- filter(data0304,direction_id == 0 & to_stop_id == 70001)
data0304_2 <- filter(data0304_1,end_time_sec == max(end_time_sec))

data0305 <- filter(dataq1_orange, service_date == "2022-03-05")
data0305_1 <- filter(data0305,direction_id == 0 & to_stop_id == 70001)
data0305_2 <- filter(data0305_1,end_time_sec == max(end_time_sec))

data0306 <- filter(dataq1_orange, service_date == "2022-03-06")
data0306_1 <- filter(data0306,direction_id == 0 & to_stop_id == 70001)
data0306_2 <- filter(data0306_1,end_time_sec == max(end_time_sec))

data0307 <- filter(dataq1_orange, service_date == "2022-03-07")
data0307_1 <- filter(data0307,direction_id == 0 & to_stop_id == 70001)
data0307_2 <- filter(data0307_1,end_time_sec == max(end_time_sec))

datamar <- rbind(data0301_2,data0302_2,data0303_2,data0304_2,data0305_2,data0306_2,data0307_2)
```

```{r}
# Data for April 2022
data0401 <- filter(dataq2_orange, service_date == "2022-04-01")
data0401_1 <- filter(data0401,direction_id == 0 & to_stop_id == 70001)
data0401_2 <- filter(data0401_1,end_time_sec == max(end_time_sec))

data0402 <- filter(dataq2_orange, service_date == "2022-04-02")
data0402_1 <- filter(data0402,direction_id == 0 & to_stop_id == 70001)
data0402_2 <- filter(data0402_1,end_time_sec == max(end_time_sec))

data0403 <- filter(dataq2_orange, service_date == "2022-04-03")
data0403_1 <- filter(data0403,direction_id == 0 & to_stop_id == 70001)
data0403_2 <- filter(data0403_1,end_time_sec == max(end_time_sec))

data0404 <- filter(dataq2_orange, service_date == "2022-04-04")
data0404_1 <- filter(data0404,direction_id == 0 & to_stop_id == 70001)
data0404_2 <- filter(data0404_1,end_time_sec == max(end_time_sec))

data0405 <- filter(dataq2_orange, service_date == "2022-04-05")
data0405_1 <- filter(data0405,direction_id == 0 & to_stop_id == 70001)
data0405_2 <- filter(data0405_1,end_time_sec == max(end_time_sec))

data0406 <- filter(dataq2_orange, service_date == "2022-04-06")
data0406_1 <- filter(data0406,direction_id == 0 & to_stop_id == 70001)
data0406_2 <- filter(data0406_1,end_time_sec == max(end_time_sec))

data0407 <- filter(dataq2_orange, service_date == "2022-04-07")
data0407_1 <- filter(data0407,direction_id == 0 & to_stop_id == 70001)
data0407_2 <- filter(data0407_1,end_time_sec == max(end_time_sec))

dataapr <- rbind(data0401_2,data0402_2,data0403_2,data0404_2,data0405_2,data0406_2,data0407_2)
```

```{r}
# Data for May 2022
data0501 <- filter(dataq2_orange, service_date == "2022-05-01")
data0501_1 <- filter(data0501,direction_id == 0 & to_stop_id == 70001)
data0501_2 <- filter(data0501_1,end_time_sec == max(end_time_sec))

data0502 <- filter(dataq2_orange, service_date == "2022-05-02")
data0502_1 <- filter(data0502,direction_id == 0 & to_stop_id == 70001)
data0502_2 <- filter(data0502_1,end_time_sec == max(end_time_sec))

data0503 <- filter(dataq2_orange, service_date == "2022-05-03")
data0503_1 <- filter(data0503,direction_id == 0 & to_stop_id == 70001)
data0503_2 <- filter(data0503_1,end_time_sec == max(end_time_sec))

data0504 <- filter(dataq2_orange, service_date == "2022-05-04")
data0504_1 <- filter(data0504,direction_id == 0 & to_stop_id == 70001)
data0504_2 <- filter(data0504_1,end_time_sec == max(end_time_sec))

data0505 <- filter(dataq2_orange, service_date == "2022-05-05")
data0505_1 <- filter(data0505,direction_id == 0 & to_stop_id == 70001)
data0505_2 <- filter(data0505_1,end_time_sec == max(end_time_sec))

data0506 <- filter(dataq2_orange, service_date == "2022-05-06")
data0506_1 <- filter(data0506,direction_id == 0 & to_stop_id == 70001)
data0506_2 <- filter(data0506_1,end_time_sec == max(end_time_sec))

data0507 <- filter(dataq2_orange, service_date == "2022-05-07")
data0507_1 <- filter(data0507,direction_id == 0 & to_stop_id == 70001)
data0507_2 <- filter(data0507_1,end_time_sec == max(end_time_sec))

datamay <- rbind(data0501_2,data0502_2,data0503_2,data0504_2,data0505_2,data0506_2,data0507_2)
```

```{r}
# Data for June 2022
data0601 <- filter(dataq2_orange, service_date == "2022-06-01")
data0601_1 <- filter(data0601,direction_id == 0 & to_stop_id == 70001)
data0601_2 <- filter(data0601_1,end_time_sec == max(end_time_sec))

data0602 <- filter(dataq2_orange, service_date == "2022-06-02")
data0602_1 <- filter(data0602,direction_id == 0 & to_stop_id == 70001)
data0602_2 <- filter(data0602_1,end_time_sec == max(end_time_sec))

data0603 <- filter(dataq2_orange, service_date == "2022-06-03")
data0603_1 <- filter(data0603,direction_id == 0 & to_stop_id == 70001)
data0603_2 <- filter(data0603_1,end_time_sec == max(end_time_sec))

data0604 <- filter(dataq2_orange, service_date == "2022-06-04")
data0604_1 <- filter(data0604,direction_id == 0 & to_stop_id == 70001)
data0604_2 <- filter(data0604_1,end_time_sec == max(end_time_sec))

data0605 <- filter(dataq2_orange, service_date == "2022-06-05")
data0605_1 <- filter(data0605,direction_id == 0 & to_stop_id == 70001)
data0605_2 <- filter(data0605_1,end_time_sec == max(end_time_sec))

data0606 <- filter(dataq2_orange, service_date == "2022-06-06")
data0606_1 <- filter(data0606,direction_id == 0 & to_stop_id == 70001)
data0606_2 <- filter(data0606_1,end_time_sec == max(end_time_sec))

data0607 <- filter(dataq2_orange, service_date == "2022-06-07")
data0607_1 <- filter(data0607,direction_id == 0 & to_stop_id == 70001)
data0607_2 <- filter(data0607_1,end_time_sec == max(end_time_sec))

datajun <- rbind(data0601_2,data0602_2,data0603_2,data0604_2,data0605_2,data0606_2,data0607_2)
```

```{r}
# Data for July 2022
data0701 <- filter(dataq3_orange, service_date == "2022-07-01")
data0701_1 <- filter(data0701,direction_id == 0 & to_stop_id == 70001)
data0701_2 <- filter(data0701_1,end_time_sec == max(end_time_sec))

data0702 <- filter(dataq3_orange, service_date == "2022-07-02")
data0702_1 <- filter(data0702,direction_id == 0 & to_stop_id == 70001)
data0702_2 <- filter(data0702_1,end_time_sec == max(end_time_sec))

data0703 <- filter(dataq3_orange, service_date == "2022-07-03")
data0703_1 <- filter(data0703,direction_id == 0 & to_stop_id == 70001)
data0703_2 <- filter(data0703_1,end_time_sec == max(end_time_sec))

data0704 <- filter(dataq3_orange, service_date == "2022-07-04")
data0704_1 <- filter(data0704,direction_id == 0 & to_stop_id == 70001)
data0704_2 <- filter(data0704_1,end_time_sec == max(end_time_sec))

data0705 <- filter(dataq3_orange, service_date == "2022-07-05")
data0705_1 <- filter(data0705,direction_id == 0 & to_stop_id == 70001)
data0705_2 <- filter(data0705_1,end_time_sec == max(end_time_sec))

data0706 <- filter(dataq3_orange, service_date == "2022-07-06")
data0706_1 <- filter(data0706,direction_id == 0 & to_stop_id == 70001)
data0706_2 <- filter(data0706_1,end_time_sec == max(end_time_sec))

data0707 <- filter(dataq3_orange, service_date == "2022-07-07")
data0707_1 <- filter(data0707,direction_id == 0 & to_stop_id == 70001)
data0707_2 <- filter(data0707_1,end_time_sec == max(end_time_sec))

datajul <- rbind(data0701_2,data0702_2,data0703_2,data0704_2,data0705_2,data0706_2,data0707_2)
```

```{r}
# Data for August 2022
data0801 <- filter(dataq3_orange, service_date == "2022-08-01")
data0801_1 <- filter(data0801,direction_id == 0 & to_stop_id == 70001)
data0801_2 <- filter(data0801_1,end_time_sec == max(end_time_sec))

data0802 <- filter(dataq3_orange, service_date == "2022-08-02")
data0802_1 <- filter(data0802,direction_id == 0 & to_stop_id == 70001)
data0802_2 <- filter(data0802_1,end_time_sec == max(end_time_sec))

data0803 <- filter(dataq3_orange, service_date == "2022-08-03")
data0803_1 <- filter(data0803,direction_id == 0 & to_stop_id == 70001)
data0803_2 <- filter(data0803_1,end_time_sec == max(end_time_sec))

data0804 <- filter(dataq3_orange, service_date == "2022-08-04")
data0804_1 <- filter(data0804,direction_id == 0 & to_stop_id == 70001)
data0804_2 <- filter(data0804_1,end_time_sec == max(end_time_sec))

data0805 <- filter(dataq3_orange, service_date == "2022-08-05")
data0805_1 <- filter(data0805,direction_id == 0 & to_stop_id == 70001)
data0805_2 <- filter(data0805_1,end_time_sec == max(end_time_sec))

data0806 <- filter(dataq3_orange, service_date == "2022-08-06")
data0806_1 <- filter(data0806,direction_id == 0 & to_stop_id == 70001)
data0806_2 <- filter(data0806_1,end_time_sec == max(end_time_sec))

data0807 <- filter(dataq3_orange, service_date == "2022-08-07")
data0807_1 <- filter(data0807,direction_id == 0 & to_stop_id == 70001)
data0807_2 <- filter(data0807_1,end_time_sec == max(end_time_sec))

dataaug <- rbind(data0801_2,data0802_2,data0803_2,data0804_2,data0805_2,data0806_2,data0807_2)
```

```{r}
# Data for September 2022
data0919 <- filter(dataq3_orange, service_date == "2022-09-19")
data0919_1 <- filter(data0919,direction_id == 0 & to_stop_id == 70001)
data0919_2 <- filter(data0919_1,end_time_sec == max(end_time_sec))

data0920 <- filter(dataq3_orange, service_date == "2022-09-20")
data0920_1 <- filter(data0920,direction_id == 0 & to_stop_id == 70001)
data0920_2 <- filter(data0920_1,end_time_sec == max(end_time_sec))

data0921 <- filter(dataq3_orange, service_date == "2022-09-21")
data0921_1 <- filter(data0921,direction_id == 0 & to_stop_id == 70001)
data0921_2 <- filter(data0921_1,end_time_sec == max(end_time_sec))

data0922 <- filter(dataq3_orange, service_date == "2022-09-22")
data0922_1 <- filter(data0922,direction_id == 0 & to_stop_id == 70001)
data0922_2 <- filter(data0922_1,end_time_sec == max(end_time_sec))

data0923 <- filter(dataq3_orange, service_date == "2022-09-23")
data0923_1 <- filter(data0923,direction_id == 0 & to_stop_id == 70001)
data0923_2 <- filter(data0923_1,end_time_sec == max(end_time_sec))

data0924 <- filter(dataq3_orange, service_date == "2022-09-24")
data0924_1 <- filter(data0924,direction_id == 0 & to_stop_id == 70001)
data0924_2 <- filter(data0924_1,end_time_sec == max(end_time_sec))

data0925 <- filter(dataq3_orange, service_date == "2022-09-25")
data0925_1 <- filter(data0925,direction_id == 0 & to_stop_id == 70001)
data0925_2 <- filter(data0925_1,end_time_sec == max(end_time_sec))

datasep <- rbind(data0919_2,data0920_2,data0921_2,data0922_2,data0923_2,data0924_2,data0925_2)
```

### Plotting and Brief Explanations 

Here are the plots showing the travel time for selected dates in each month.  

```{r}
# Plot for October 2021
ggplot(data = dataoct) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

There are only six dates contained in this plot. The reason is that there were no lines which satisfied my selection for the missing day. 

```{r}
#Plot for November 2021
ggplot(data = datanov) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for December 2021
ggplot(data = datadec) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for January 2022
ggplot(data = datajan) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for Febuary 2022
ggplot(data = datafeb) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for March 2022
ggplot(data = datamar) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for April 2022
ggplot(data = dataapr) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time")
```

```{r}
# Plot for May 2022
ggplot(data = datamay) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for June 2022
ggplot(data = datajun) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for July 2022
ggplot(data = datajul) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for August 2022
ggplot(data = dataaug) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

```{r}
# Plot for September 2022
ggplot(data = datasep) + 
  aes(x = service_date, y = travel_time_sec) + 
  geom_line() +
  geom_point(aes(x = service_date, y = travel_time_sec,color = factor(service_date),group = 1)) + 
  ggtitle(label = "Travel Time") +
  theme(axis.text.x = element_text(size = 7))
```

The points on the same line had the same direction and the same destination. Different starting stops led to different travel times. Each line showed the distribution of travel time on the same day and each plot showed weekly distribution of travel time based on my selection. 

To avoid the situation of having too many points on one line so that all points could not be seen clearly, I filtered the data with some criteria to show the distribution under one specific situation. Other situations can be shown using similar methods.